Roster Review (Generic)

### 2019-07-09 rosterReview_generic.Rmd
WIP implementing optimal lineup

optimal_lineups_offense <- rosters_by_position %>% 
  optimal_lineup()

@@

```{r}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos

ggplotly(team_pos)

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  filter(grepl("Plouffe",team)) %>% 
  arrange(pos_zar %>% desc) %>%
  mutate(pos_zar = pos_zar %>% round(1),
         zar = zar %>% round(1)) %>% 
  View("ZAR by Position")

@@

# FIXME join optimal offense lineup with all pitching
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  group_by(team, position) %>% 
  summarize(avg_pos_zar = mean(pos_zar)) -> team_pos_avg_zar

team_pos_avg_zar %>%  
  ggplot(aes(position, avg_pos_zar, color = position)) +
  geom_point() +
  facet_wrap(~ team) -> team_avg_pos

ggplotly(team_avg_pos)

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(avg_pos_zar),
            mean_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(mean_pos_zar %>% desc)

rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(pos_zar)) + 
  geom_freqpoly(binwidth=.25) + 
  facet_wrap(~ position)
```

@@

rosters %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
  geom_boxplot()
```

>>>>

team_batters_starters <- rosters_by_position %>% 
  optimal_lineup()

# TODO get position factor ordering back, summarize pitching to single point/range, add bench single point/range, consider DL?
rosters_by_position %>% 
  filter(team != "Free Agent",
         type == "pitcher") %>% 
  mutate(position = as.character(position)) %>% 
  droplevels() -> team_pitchers_all

team_pitchers_SP <- team_pitchers_all %>% 
  filter(position == 'SP')

team_pitchers_RP <- team_pitchers_all %>% 
  filter(position == 'RP') %>% 
  anti_join(team_pitchers_SP, "player_id") %>% 
  group_by(team) %>% 
  arrange(zar %>% desc) %>% 
  mutate(rnk = row_number()) %>% 
  filter(rnk <= 6) %>% 
  select(position, player_id, name_full, team, manager, zar, pos_zar)

team_pitchers_SP %>% 
  bind_rows(team_pitchers_RP) %>% 
  group_by(team, position) %>% 
  summarize(zar = mean(zar),
            pos_zar = mean(pos_zar)) -> team_pitchers_starters

rosters_by_position %>% 
  filter(team != "Free Agent",
         type == "batter") %>% 
  mutate(position = as.character(position)) %>% 
  droplevels() -> team_batters_all

team_batters_all %>% 
  anti_join(team_batters_starters, "player_id") %>% 
  group_by(player_id, name_full) %>% 
  arrange(player_id, pos_zar %>% desc) %>% 
  mutate(rnk = row_number(),
         position = "BN") %>% 
  filter(rnk == 1) %>% 
  ungroup() %>% 
  select(position, player_id, name_full, team, manager, zar, pos_zar) -> team_batters_bench

team_batters_starters %>% 
  bind_rows(team_batters_bench) %>% 
  bind_rows(team_pitchers_starters)

#FIXME team_batters_starters needs MANAGER column

@@

```{r}
rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  filter(grepl("Plouffe",team)) %>% 
  arrange(pos_zar %>% desc) %>%
  mutate(pos_zar = pos_zar %>% round(1),
         zar = zar %>% round(1)) %>% 
  View("ZAR by Position")

@@

team_pitchers %>% 
  bind_rows(team_batters_starters) %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point() +
  facet_wrap(~ team) -> team_pos_optimal

ggplotly(team_pos_optimal)

team_pos_avg_zar %>% 
  ungroup() %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(avg_pos_zar),
            mean_pos_zar = mean(avg_pos_zar),
            var_pos_zar = sd(avg_pos_zar)) %>% 
  arrange(mean_pos_zar %>% desc)
```

@@

rosters %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  arrange(draft_round) %>% 
  ggplot(aes(x=draft_round,y=war,group=draft_round)) +
  geom_boxplot()

# frequency graph by pos_zar for each position
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(pos_zar)) + 
  geom_freqpoly(binwidth=.25) + 
  facet_wrap(~ position)
```
